### 2022-01-06 README.Rmd
Trying to set up docker and travis

[![Binder](https://mybinder.org/badge_logo.svg)](https://mybinder.org/v2/gh/isakro/dialpastrepository/master?urlpath=rstudio)

@@

The simplest way to explore the text, code and data is to click on
[binder](https://mybinder.org/v2/gh/isakro/dialpastrepository/master?urlpath=rstudio)
to open an instance of RStudio in your browser, which will have the
compendium files ready to work with. Binder uses rocker-project.org
Docker images to ensure a consistent and reproducible computational
environment. These Docker images can also be used locally.

>>>>

[![Binder](https://mybinder.org/badge_logo.svg)](https://mybinder.org/v2/gh/isakro/exploring-assemblages-se-norway/master?urlpath=rstudio)

@@

The simplest way to explore the text, code and data is to click on
[binder](https://mybinder.org/v2/gh/isakro/exploring-assemblages-se-norway/master?urlpath=rstudio)
to open an instance of RStudio in your browser, which will have the
compendium files ready to work with. Binder uses rocker-project.org
Docker images to ensure a consistent and reproducible computational
environment. These Docker images can also be used locally.
